---
title: "DataManagement1"
author:
date: Fall 2015
output: html_document
---

```{r, echo = FALSE, message = FALSE}
knitr::opts_chunk$set(comment = NA, message = FALSE, warning = FALSE, fig.align = "center")
library(ggplot2)
library(descr)
```

Three categorical variables relevant to student health are H1SU1-H1SU3 from the AddHealth data set. The AddHealth data set is loaded from the PDS package. Using the dplyr package, a new data frame NDF containing only three variables after renaming H1SU1-H1SU3 to Absences, Last physical examination and Last math grade is created.

```{r}
library(PDS)
library(dplyr)
NDF <- AddHealth %>%
  rename(Absences = H1ED1, HoursofSleep = H1GH51, LastPhyExam = H1GH24, LastMathGrade = H1ED12) %>%  
  select(Absences, HoursofSleep, LastPhyExam, LastMathGrade)
head(NDF)
```

Responses of `9` for question `Absences` are recorded to `NA`

```{r}
xtabs(~Absences, data = NDF)
NDF$Absenses[NDF$Absences == 9] <- NA
xtabs(~Absences, data = NDF)
NDF$Absences <- factor(NDF$Absences, labels = c("never", "1 or 2 times","3 to 10 times", "more than 10 times", "refused", "legitiment skip", "don't know", "not applicable")
xtabs(~Absences, data = NDF)
summary(NDF$Absences)
freq(NDF$Absences)
freq(NDF$Absences, main = "How many absences have you had?")
ggplot(data = NDF, aes(x = Absences, fill = Absences)) + 
  geom_bar() + 
  labs(title = "How many absences have you had?", x = "") +
  theme_bw() +
  guides(fill = guide_legend(title = "How many absences have you had?"))
```
Changing the $y$-axis to percent:

```{r}
ggplot(data = NDF, aes(x = Absences, y = (..count..)/sum(..count..), fill = Absences)) + 
  geom_bar() + 
  labs(title = "How many absences have you had?", x = "") +
  theme_bw() +
  guides(fill = guide_legend(title = "How many absences have you had")) +
  labs(y = "percent")
```

Another approach to graph the catagorical variables is to use the base fuction `barplot()`.
```{r}
barplot(xtabs(~Absences, data = NDF), col = c("green", "red", "orange", "brown"))
barplot(prop.table(xtabs(~Absences, data = NDF)), col = c("green", "red", "orange", "brown"))
```
